Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-23 paper.tex
a little proof, a few revision

\begin{proposition}[$L$ properties]\ 
  \begin{enumerate}
  \item $L$ is an instance of the Lazy D ADT
  \item $L$ is a monoid
  \item $cast(T,l,T) = id(T)$
  \end{enumerate}
\end{proposition}

\begin{lemma}[$L$ is correct wrt. \ineffCEKD]
  \label{lem:L-correct}
  \[
  \text{\evalEqv{\effCEK{L}}{\ineffCEKD}}
  \]
\end{lemma}

@@

\begin{lemma}[\lazyD{} hypercoercion is a \lazyD Cast ADT]
	\label{thm:hc-surely-lazyD}
\end{lemma}
\begin{proof} See the supplementary material. \end{proof}

>>>>

\begin{proposition}[$L$ properties]\label{thm:L-LazyD-monoid}\ 
  \begin{enumerate}
  \item $L$ is an instance of the Lazy D ADT
  \item $L$ is a monoid
  \item $cast(T,l,T) = id(T)$
  \end{enumerate}
\end{proposition}
\begin{proof}
	Part (1) is straightforward because property (1) and (2) are trivial and 
	that $appS$ basically repeats property (3) - (11).
	Part (2) is true because in $L$ casts are list, $seq(c,c)$ is list 
	appending, and $id(T)$ is the empty list. Lists is know to be a monoid 
	where the binary operation is appending and the identity element is the 
	empty list.
	Part (3) follows immediately from the definition of $cast(T,l,T)$
\end{proof}

\begin{lemma}[$L$ is correct wrt. \ineffCEKD]
  \label{lem:L-correct}
  \[
  \text{\evalEqv{\effCEK{L}}{\ineffCEKD}}
  \]
\end{lemma}
\begin{proof}
	Immedialy from Correctness of \effCEK{C} \ref{thm:surely-monoidic-eval} and 
	L properties \ref{thm:L-LazyD-monoid}.
\end{proof}

@@

\begin{lemma}[\lazyD{} hypercoercion is a \lazyD{} Cast ADT]
	\label{thm:hc-surely-lazyD}
\end{lemma}
\begin{proof} See the supplementary material. \end{proof}
